---
title: "Homework1"
author: "Xueying_Li&Huiqiong_Liao"
date: "1/25/2018"
output:
  pdf_document: default
  html_document: default
abstract: |
  We used Monte Carlo method to estimate the value of the distribution of N(0,1) at        $n \in \{10^2,10^3,10^4\}$ at $t \in                                                    \{0.0,0.67,0.84,1.28,1.65,2.32,2.58,3.09,3.72\}$. Then we formed the table consisting the mean value of 100 times the experiments and the true value. Also, we generated the box plots of the bias at all t.
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The application of Monte Carlo methods 

The distribution function of $N(0, 1)$, 
\begin{equation}
\Phi(t) = \int_{-\infty}^t \frac{1}{\sqrt{2\pi}} e^{-y^2 / 2} dy,
\tag{1.1}
\end{equation}

We applied the formula below to estimate the value of the formula 1.1.
\begin{equation}
\hat\Phi(t) = \frac{1}{n} \sum_{i=1}^n I(X_i \le t),
\tag{1.2}
\end{equation}

where $X_i$'s are iid $N(0, 1)$ variables. We wrote the function phi_cal to calculate the $\hat\Phi(t)$ given specific t and n. The R code chunk works like this:

```{r}
phi_cal <- function(t,n){
  x <- rnorm(n,0,1)
  I_x <- array(n)
  for (i in 1:n) {
    if(x[i]>t)
      I_x[i] <- 0
    else
      I_x[i] <- 1
  }
  phi <- sum(I_x)/n
  return(phi)
}
```

Similarly, we wrote the function phi_real to get the real value of the cdf of $N(0, 1)$. The R code chunk works like this:
```{r}
phi_real <- function(t){
  y <- pnorm(t,0,1)
  return(y)
}
```

Next, we repeated the experiment for 100 times and drew the box plots of the bias at all t. The results are shown in the following three pictures.

```{r, echo=FALSE,eval=TRUE,out.width='50%',fig.show='hold'}
rm(list=ls())
n <- c(100,1000,10000)
t <- c(0.0,0.67,0.84,1.28,1.65,2.32,2.58,3.09,3.72)

phi_cal <- function(t,n){
  x <- rnorm(n,0,1)
  I_x <- array(n)
  for (i in 1:n) {
    if(x[i]>t)
      I_x[i] <- 0
    else
      I_x[i] <- 1
  }
  phi <- sum(I_x)/n
  return(phi)
}

phi_real <- function(t){
  y <- pnorm(t,0,1)
  return(y)
}

# phi_cal_mean <- function(t,n){
#   phi=array()
#   for(i in 1:100){
#     phi[i] <- phi_cal(t,n)
#   }
#   phi_mean <- mean(phi)
#   return(phi_mean)
# }
x <- array(0,dim=c(length(n),length(t),100))
for(k in 1:100){
  for (i in 1:length(n)) {
    for (j in 1:length(t)) {
      x[i,j,k] <- phi_cal(t[j],n[i])
    }
  }
}
#str(x)
boxplot(x[1, , ]~t)
boxplot(x[2, , ]~t)
#boxplot(x[3, , ]~t)
# boxplot(x[1:2, , ]~t*t)
```
```{r, autodep = TRUE, eval=TRUE, echo=FALSE, fig.show='hold', out.width='50%'}
boxplot(x[3, , ]~t)
```

Finally, we calculated the mean of the **phi_cal** by using table to demonstrate the results compared to the real value of the normal distribution. The first three lines from the table are corresponded to n = 100, 1000, 10000 respectively, while the last line reveals the real value. Here is the table:

```{r, echo=FALSE,eval=TRUE}
#rm(list=ls())
n <- c(100,1000,10000)
t <- c(0.0,0.67,0.84,1.28,1.65,2.32,2.58,3.09,3.72)

phi_cal <- function(t,n){
  x <- rnorm(n,0,1)
  I_x <- array(n)
  for (i in 1:n) {
    if(x[i]>t)
      I_x[i] <- 0 
    else
      I_x[i] <- 1
  }
  phi <- sum(I_x)/n
  return(phi)
}

phi_real <- function(t){
  y <- pnorm(t,0,1)
  return(y)
}

phi_cal_mean <- function(t,n){
  phi=array()
  for(i in 1:100){
    phi[i] <- phi_cal(t,n)
  }
  phi_mean <- mean(phi)
  return(phi_mean)
}

x <- array(0,dim=c(length(n)+1,length(t)))
for (i in 1:length(n)) {
  for (j in 1:length(t)) {
    x[i,j] <- phi_cal_mean(t[j],n[i])
  }
}
#str(x)
for(j in 1:length(t)){
  x[length(n)+1,j] <- phi_real(t[j])
}
row_name <- c("n=100","n=1000","n=10000","real_value")
table <- as.data.frame(x,row.names = row_name)
knitr::kable(table, col.names = t,row.names = TRUE)
```